\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{parskip}

% Customize section titles
\titleformat{\section}{\large\bfseries}{\thesection}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% Remove page numbering
\pagestyle{empty}

\begin{document}

% Header
\begin{center}
    {\Large \textbf{Nurkhan Masimzada}} \\
     Warsaw, Poland - Baku, Azerbaijan \\
    +48 573 403 395 | nmasimzade@outlook.com | LinkedIn | Portfolio
\end{center}

\section*{Career Objectives}
\begin{itemize}[leftmargin=*]
 
    \item Seeking challenging roles that involve working with multilingual teams and international projects.
    \item Applying and enhancing knowledge of various programming languages, frameworks, and technologies (C\#, ASP.NET, SQL, Python, Django, HTML, CSS, JavaScript, React.js).
    \item Contributing to the creation and maintenance of scalable, user-focused systems.
    \item Gaining further experience in quality assurance, debugging, and issue tracking.
    \item Leveraging existing experience in both front-end and back-end development, as well as teaching/mentoring roles.
    \item Furthering academic knowledge while gaining practical experience in the software development field (M.Sc. in Computer Science).
\end{itemize}

\section*{Relevant Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Languages}: English (Professional), Polish (Intermediate), Turkish (Native),  Azerbaijani (Native)
    \item \textbf{Software Skills}: C\#, ASP.NET, SQL, Python, Django, HTML, CSS, JavaScript, React.js
    \item \textbf{Transferrable Skills}: Attention to detail, debugging, user-focused design, multi-platform understanding
    \item \textbf{Soft Skills}: Communication, team collaboration, problem-solving
    \item \textbf{Tech Knowledge}: Experience with browser tools, mobile interfaces
\end{itemize}

\section*{Professional Experience}

\textbf{Life-Doc Sp. z o.o.} — \textit{Full-Stack Software Developer} \\
Warsaw, Poland | Feb 2025 – May 2025
\begin{itemize}[leftmargin=*]
    \item Developed multiple CRM systems with cross-language interface support
    \item Collaborated with multilingual teams, ensuring software compatibility in different regions
    \item Gained hands-on experience in quality assurance and issue tracking
\end{itemize}

\textbf{Nesla Construction Sp. z o.o.} — \textit{Software Engineer} \\
Warsaw, Poland | Nov 2023 – Nov 2024
\begin{itemize}[leftmargin=*]
    \item Built and maintained scalable systems with a focus on user experience
    \item Frequently debugged and resolved system errors, requiring precision and analytical thinking
    \item Gained insight into multilingual UI/UX feedback through internal testing
\end{itemize}


\textbf{Baku IT Academy} — \textit{Programming Instructor} \\
Baku | Jan 2023 – Jul 2023
\begin{itemize}[leftmargin=*]
    \item Taught HTML, C\#, React.js, and more to students
    \item Built real-world projects with students, simulating bug tracking and testing environments
\end{itemize}



\section*{Education}

\textbf{WSB University} — M.Sc. in Computer Science (Ongoing) \\
Poland | Oct 2023 – May 2025

\textbf{Azerbaijan University of Architecture and Construction} — B.Sc. in Computer Engineering \\
Azerbaijan | Sep 2019 – Jun 2023

\textbf{Code Academy} — Software Development \\
Azerbaijan | Feb 2021 – Dec 2022

\section*{Certifications}
\begin{itemize}[leftmargin=*]
    \item AWS Academy Graduate / Cloud Foundations - Amazon AWS
    \item Software Development Diploma High Honour - Code Academy
    \item Rate Limiting with Cloud Armor - Google
    \item A-Z ChartJS Course (2022)
\end{itemize}

\end{document}